# Reproducible Research: Peer Assessment 1

## Loading and preprocessing the data
```{r}
library(lattice)
x <- read.csv(unz('activity.zip', 'activity.csv'))
x$date <- as.Date(x$date)
```

## What is mean total number of steps taken per day?
```{r}
## summing steps for each day
perDay <- aggregate(x$steps, list(date=x$date), sum, na.rm=TRUE)
histogram(perDay$x,
          main='Histogram of total number of steps taken each day',
          xlab='steps')
```
#### mean total number of steps taken per day
```{r}
mean(perDay$x)
```
#### median total number of steps taken per day
```{r}
median(perDay$x)
```


## What is the average daily activity pattern?
```{r}
## getting mean of steps for each interval
perInterval <- aggregate(x$steps, list(interval=x$interval), mean, na.rm=TRUE)
xyplot(x ~ interval,
       data=perInterval,
       type='l',
       xlab='5-minute interval',
       ylab='average number of steps')
```
#### 5-minute interval with maximum number of steps
```{r}
perInterval$interval[which.max(perInterval$x)]
```


## Imputing missing values
#### total number of missing values
```{r}
missing <- is.na(x$steps)
sum(missing)
```

#### filling missing values with mean for the same interval
mean values are already calculated in perInterval dataset
```{r}
missingInterval <- x[missing, 'interval']
meanSteps <- sapply(missingInterval,
                    function(z) round(perInterval$x[which(perInterval$interval == z)]))
```

#### creating new dataset with filled in missing values
```{r}
y <- x
y[missing, 'steps'] <- meanSteps
```

#### histogram, mean and median for dataset with filled in missing values
```{r}
perDayY <- aggregate(y$steps, list(date=y$date), sum)
histogram(perDayY$x,
          main='Histogram of total number of steps taken each day',
          xlab='steps')
mean(perDayY$x)
median(perDayY$x)
```

## Are there differences in activity patterns between weekdays and weekends?

```{r}
getDayType <- function(z){
        d = weekdays(z)
        if(d == 'Sunday' || d == 'Saturday') 'weekend'
        else 'weekday'
}
y$dayType <- factor(sapply(y$date, getDayType))

## getting mean of steps for each interval and each day type
perDayType <- aggregate(y$steps, list(interval=y$interval, dayType=y$dayType), mean)
xyplot(x ~ interval | dayType,
       data=perDayType,
       type='l',
       ylab='Number of steps',
       layout=c(1, 2))
```
