# Reproducible Research: Peer Assessment 1
```{r setoptions, echo=FALSE}
opts_chunk$set(echo=TRUE)
```


## Loading and preprocessing the data
```{r}
x <- read.csv(unz('activity.zip', 'activity.csv'))
x$date <- as.Date(x$date)
```


## What is mean total number of steps taken per day?
```{r}
perDay <- aggregate(x$steps, list(date=x$date), sum, na.rm=TRUE)
hist(perDay$x, main='Histogram of total number of steps taken each day', xlab='steps')
```
#### mean total number of steps taken per day
```{r}
mean(perDay$x)
```
#### median total number of steps taken per day
```{r}
median(perDay$x)
```


## What is the average daily activity pattern?
```{r}
perInterval <- aggregate(x$steps, list(interval=x$interval), mean, na.rm=TRUE)
plot(perInterval, type='l', xlab='5-minute interval', ylab='average number of steps')
```
#### 5-minute interval with maximum number of steps
```{r}
perInterval$interval[which.max(perInterval$x)]
```



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
